{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-15 paper.tex
IEEEtrans template (for RSS)

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[HRI2018]{ACM/IEEE Human-Robot Conference}{March 2018}{Chicago USA} 
\acmYear{2018}
\copyrightyear{2018}

\acmArticle{4}
\acmPrice{15.00}

%\author{Séverin Lemaignan$^{*}$, Fotios Papadopoulos$^{*}$%
%\thanks{$^{*}$Authors are with Centre for Robotics and Neural Systems,
%        Plymouth University, Plymouth PL48AA, United Kingdom
%        {\tt\small firstname.surname@plymouth.ac.uk}}%
%}

\author{[Hidden for review]}
\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{xxx}
%  \streetaddress{xxx}
%  \city{Dublin} 
%  \state{Ohio} 
%  \postcode{43017-6221}
%}
%\email{trovato@corporation.com}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010520.10010553.10010554</concept_id>
<concept_desc>Computer systems organization~Robotics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Robotics}

\keywords{Human-Robot Interaction, Situation Assessment, Perspective Taking}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

@@

\maketitle
%\thispagestyle{empty}
%\pagestyle{empty}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}

\usepackage{graphicx}
\usepackage{booktabs} % For formal tables

\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

\pdfinfo{
   /Author (Hidden for blind review)
   /Title  (underwords: Cascading Situation Assessment for Robots)
   /CreationDate (D:20180115162200)
   /Subject (Robots)
   /Keywords (Situation Assessment;Perspective Taking)
}

@@

\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

%\author{\authorblockN{Séverin Lemaignan}
%\authorblockA{Centre for Robotics and Neural Systems\\
%University of Plymouth\\
%Plymouth, United Kingdom\\
%Email: severin.lemaignan@plymouth.ac.uk}
%\and
%\authorblockN{Yoan Sallami, Aurélie Clodic and Rachid Alami}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

\begin{abstract}

@@

\IEEEpeerreviewmaketitle

@@

\bibliographystyle{plainnat}
\bibliography{bibliography}
